---
title: "Data Science: Everyday Music Listening"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

# I am a big heading
## I am a smaller heading
## I am an even smaller heading
 
Normal *italic* **bold** text.

- List
- Another list
```{r}
library(tidyverse)
library(spotifyr)
source('spotify.R')
```

```{r}
get_playlist_audio_features('spotify','37i9dQZF1DXcBWIGoYBM5M')
```

```{r}
spotify_features <-

tribble(
  ~type, ~subtype, ~user, ~playlist
  'Studying', 'Instrumental', 'spotify', '37i9dQZF1DX9sIqqvKsjG8',
    'Studying', 'Intense', 'spotify', '37i9dQZF1DX8NTLI2TtZa6',
    'Concentration', 'Electronic', 'spotify', '37i9dQZF1DX3XuTDjo5z5z',
    'Concentration', 'Natural', 'spotify', '37i9dQZF1DWYFCj3KyU0r0'
  ) %>% 


```


This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
